---
title: "Udacity_Lesson7_ExploreManyVariables"
author: "Armir Kaçabeti"
date: "7 Nisan 2018"
output: pdf_document
---

#title: "Udacity_Lesson7_ExploreManyVariables"
#author: "Armir Kaçabeti"

### Lesson 7: Explore Many Variables

###Third Qualitative Variable
```{r}
library(ggplot2)
pf <- read.csv('pseudo_facebook.tsv', sep = '\t')
ggplot(aes(x = gender, y = age),
       data = subset(pf, !is.na(gender))) + geom_boxplot() +
  stat_summary(fun.y = mean, geom = 'point', shape = 4)
```

```{r}
ggplot(aes(x = age, y = friend_count),
       data = subset(pf, !is.na(gender))) +
  geom_line(aes(color = gender), stat = 'summary', fun.y = median)
```
#Q1
```{r}
library(dplyr)

age_gender_group <- group_by(pf, age, gender)
age_gender_group <- filter(age_gender_group, !is.na(gender))
pf.fc_by_age_gender <- summarise(age_gender_group,
                                 mean_friend_count = mean(friend_count),
                                 median_friend_count = median(friend_count),
                                 n = n())
arrange(pf.fc_by_age_gender, age)
```

```{r}
head(pf.fc_by_age_gender, 10)
```
#Q2
### Plotting Conditional Summaries 
```{r}
ggplot(data = pf.fc_by_age_gender, aes(x = age, y = median_friend_count)) + geom_line(aes(color = gender), stat = 'summary', fun.y = median)
```

### Reshaping Data
```{r}
#install.packages('reshape2')
library(reshape2)

pf.fc_by_age_gender.wide <- dcast(pf.fc_by_age_gender,
                                  age ~ gender,
                                  value.var = 'median_friend_count')

head(pf.fc_by_age_gender.wide)
```

```{r}
### Alternative code with dplyr and tidyr
library(dplyr)
#install.packages('tidyr')
library(tidyr)
pf.fc_by_age_gender.wide <-     subset(pf.fc_by_age_gender[c('age', 'gender', 'median_friend_count')],                   !is.na(gender)) %>% 
    spread(gender, median_friend_count) %>% 
    mutate(ratio = male / female) 

head(pf.fc_by_age_gender.wide)
```
#Q3
### Ratio Plot
```{r}
ggplot(data = pf.fc_by_age_gender.wide, aes(x = age, y = female / male)) +
  geom_line() +
  geom_hline(yintercept = 1, alpha = 0.3, linetype = 2)
```
#Q4
### Third Quantitative Variable
```{r}
pf$year_joined <- floor(2014 - pf$tenure/365)
```

### Cut a Variable
```{r}
summary(pf$year_joined)
```

```{r}
table(pf$year_joined)
```

```{r}
#?cut
```
#Q5
```{r}
pf$year_joined.bucket <- cut(pf$year_joined, c(2004, 2009, 2011, 2012, 2014))
```

### Plotting it All Together
```{r}
table(pf$year_joined.bucket, useNA = 'ifany')
```

```{r}
ggplot(data = subset(pf, !is.na(year_joined.bucket)), aes(x= age, y=friend_count)) +
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = median)
```

### Plot the Grand Mean
```{r}
ggplot(data = subset(pf, !is.na(year_joined.bucket)), aes(x= age, y=friend_count)) +
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = mean) +
  geom_line(stat = 'summary', fun.y = mean, linetype = 2)
```

### Friending Rate
```{r}
with(subset(pf, tenure >= 1), summary(friend_count / tenure))
```

### Friendships Initiated
```{r}
ggplot(data = subset(pf, tenure >= 1), aes(x= tenure, y=friendships_initiated / tenure)) +
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = mean)
```

### Bias-Variance Tradeoff Revisited
```{r}
ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)
```

```{r}
ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_smooth(aes(color = year_joined.bucket))
```

```{r}
ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)
```

```{r}
ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)
```

### Histograms Revisited
```{r}
yo <- read.csv("yogurt.csv")
qplot(data = yo, x = price, fill = I('#F79420'))

```

### Number of Purchases
```{r}
summary(yo)
```

```{r}
unique(yo$price)
```

```{r}
length(unique(yo$price))
```

```{r}
table(yo$price)
```

```{r}
yo <- transform(yo, all.purchases = strawberry + blueberry + 
                  pina.colada + plain + mixed.berry)

summary(yo$all.purchases)
```

### Prices over Time
```{r}
qplot(x = all.purchases, data = yo, binwidth = 1,
      fill = I('#099DD9'))
```

```{r}
ggplot(data = yo, aes(x = time, y = price)) + 
  geom_jitter(alpha = 1/4, shape = 21, fill = I('#F79420'))
```

### Looking at Samples of Households
```{r}
set.seed(2056)
sample_id <- unique(yo$id)
sample.ids <- sample(x = sample_id, size = 16)

ggplot(aes(x = time, y = price),
       data = subset(yo, id %in% sample.ids)) +
  facet_wrap( ~ id) +
  geom_line() +
  geom_point(aes(size = all.purchases), pch = 1)
```

### Scatterplot Matrix
```{r}
#install.packages("GGally")
library(GGally)

theme_set(theme_minimal(20))

# set the seed for reproducible results
set.seed(1836)
pf_subset <- pf[, c(2:15)]
names(pf_subset)

```

```{r}
ggpairs(pf_subset[sample.int(nrow(pf_subset), 1000), ])
```

### Heat Maps
```{r}
nci <- read.table("nci.tsv")
colnames(nci) <- c(1:64)

nci.long.samp <- melt(as.matrix(nci[1:200,]))
names(nci.long.samp) <- c("gene", "case", "value")
head(nci.long.samp)
```

```{r}
ggplot(aes(y = gene, x = case, fill = value),
  data = nci.long.samp) +
  geom_tile() +
  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))
```

